---
title: "Social-Media und Text-Mining-Workshop mit R"
subtitle: "Konzeptionelle Grundlagen & Herausforderungen bei der Analyse von Social-Web-Daten"
author: "Veronika Batzdorfer"
date: '2022-09-29'
presenter: Veronika

---
layout: true 

```{r child = "./content/config/sessions_setup.Rmd"}
```

---

## About this course

In this course, we will provide an introduction to the basic concepts and functionalities of `R` and go through a prototypical data analysis workflow: import, wrangling, exploration, (basic) analysis, and reporting. 

By the end of this course you should...

- be comfortable with using `R` and *RStudio*
- be able to import, wrangle, and explore your data with `R`
- be able to create/conduct basic visualizations and analyses of your data with `R`
- be able to generate reproducible research reports using `R Markdown`

--

**Note**: This is not a statistics workshop. Our focus will be on learning how to use `R`.

---

## Working with `R` - Whole game


---

## Prerequisites for this course

.large[
- Working versions of `R` (>= version 4.0.0) and *RStudio* on your computer 

- Prior experience with quantitative data analysis, basic statistics, and regression 

- Experience with using other statistical packages (e.g., *SPSS* or *Stata*) is helpful
]  

---
## About us: Veronika Batzdorfer

.pull-left[
```{r veronika-pic, echo = FALSE, out.width = "50%"}
woRkshoptools::include_picture("./Veronika.jpg")
```
]

.pull-right[
- Postdoctoral researcher in the team Digital Society Observatory at the GESIS department Computational Social Science (with a secondary affiliation also in the team Survey Data Augmentation in the department Survey Data Curation)
]

.small[
- Research interests:
  - digital trace data
  - temporal dynamics on social media platforms
  - causal identification

[veronika.batzdorfer@gesis.org](mailto:veronika.batzdorfer@gesis.org) |
[Personal GESIS website](https://www.gesis.org/en/institute/staff/person/Veronika.Batzdorfer?no_cache=1)
]

---

## About you

- What's your name?  

- Where do you work/study? What are you working on/studying?

---

## Workshop Structure & Materials

- The workshop consists of a combination of lectures and hands-on exercises

- For the time after the workshop sessions each day, we have also prepared some optional (and hopefully fun) "extracurricular activities"

- Slides and other materials are available at

.center[`https://github.com/nika-akin/-Social-Media-and-Text-Mining-Workshop-2022`]








